Security Audit of Safeplug

### 2014-01-14 bibliography.tex
spymall

@@

\bibitem{tor} Dingledine, Roger, Nick Mathewson, and Paul Syverson. Tor: The second-generation onion router. NAVAL RESEARCH LAB WASHINGTON DC, 2004.

\bibitem{tor2} Johnson, Aaron, et al. ``Users get routed: Traffic correlation on Tor by realistic adversaries.'' Proceedings of the 2013 ACM SIGSAC conference on Computer & communications security. ACM, 2013.

\bibitem{fingerprint1} Cai, Xiang, et al. "Touching from a distance: Website fingerprinting attacks and defenses." Proceedings of the 2012 ACM conference on Computer and communications security. ACM, 2012.

\bibitem{fingerprint2} Kohno, Tadayoshi, Andre Broido, and Kimberly C. Claffy. "Remote physical device fingerprinting." Dependable and Secure Computing, IEEE Transactions on 2.2 (2005): 93-108.

\bibitem{commercial1} Nikiforakis, Nick, et al. "Cookieless monster: Exploring the ecosystem of web-based device fingerprinting." IEEE Symposium on Security and Privacy. 2013.

\bibitem{commercial2} Mayer, Jonathan R., and John C. Mitchell. "Third-party web tracking: Policy and technology." Security and Privacy (SP), 2012 IEEE Symposium on. IEEE, 2012.

>>>>

\bibitem{spymall} Appelbaum et. al. ``Shopping for Spy Gear: Catalog Advertises 
NSA Toolbox'' \emph{Der Spiegel} 29 December 2013 \url{www.spiegel.de/internatio
nal/world/catalog-reveals-nsa-has-back-doors-for-numerous-devices-a-940994.html}

@@
